Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Choose the color palattes for Figure 8 and color the lines accordingly

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
             aes(x = UMAP1, y = UMAP2),
             alpha = 0.3,
             size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a", position = c(0.92, 0.93)) +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2))

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2)) +
  interior_annotation("c")

@@

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.12, linetype="solid",
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.10, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

>>>>

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
             aes(x = UMAP1, y = UMAP2),
             alpha = 0.3,
             size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "E") +
  interior_annotation("a", position = c(0.92, 0.93)) +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2))

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "D") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2)) +
  interior_annotation("c")

@@

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#006d2c",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.12, linetype="solid",
             color = "#006d2c", linewidth=1) +
  geom_vline(xintercept = 0.10, linetype=2,
             color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())
